---
title: "Prelim. eval. of GW tests on Hönggerberg"
author: "Beatrice Marti"
date: "9/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library('tidyverse')
library('tidymodels')

# Options
options(digits.secs = 3)
```

# Slug test
```{r slug-test-raw, echo=FALSE, message=FALSE, warning=FALSE}
# Get data into shape
data_slug <- read.table('SlugTest_200903.csv', sep=';', skip=5,
                        na.strings='#NV', header=TRUE, 
                        col.names=c('Time_p','p_bar','Time_T','T_degC','X')) %>%
  select(-X) %>%
  mutate(Time_p=as.POSIXct(Time_p,format='%d.%m.%Y %H:%M:%OS'),
         Time_T=as.POSIXct(Time_T,format='%d.%m.%Y %H:%M:%OS')) %>%
  drop_na() %>%
  mutate(label=if_else(Time_p<=as.POSIXct("2020-09-03 15:35:57"),'baseline',
                       if_else(Time_p>=as.POSIXct("2020-09-03 15:36:11"),'test',
                       'NA'))) 

h0_slug <- data_slug %>%
  filter(label=='baseline') %>%
  select(p_bar) %>% 
  colMeans()

# Constant pressure at beginning of experiment
data_slug <- data_slug %>%
  mutate(lm=if_else(label=='baseline',as.numeric(h0_slug),NULL))

# Linear interpolation 

ggplot(data_slug) +
  geom_point(aes(Time_p,p_bar),size=0.2) + 
  geom_line(data=data_slug %>% filter(label=='baseline'), 
            aes(Time_p,lm,color=label)) + 
  ggtitle('Raw data') + 
  theme_bw()
```

```{r slug-test, echo=FALSE}
# Process time series for evaluation
data_slug <- data_slug %>%
  mutate(label=if_else(Time_p<=as.POSIXct("2020-09-03 15:35:57"),'baseline',
                       if_else(Time_p>=as.POSIXct("2020-09-03 15:36:11"),'test',
                       'NA')))
h0_slug <- data_slug %>%
  filter(label=='baseline') %>%
  select(p_bar) %>% 
  colMeans()

ht_slug <- data_slug %>%
  filter(label=='test') %>%
  select(Time_p,p_bar) %>%
  mutate(dp_bar=p_bar-h0_slug,
         dt=c(0,diff(Time_p,lag=1)),
         Time_s=cumsum(dt)) %>%
  filter(Time_s>0)

ggplot(ht_slug) +
  geom_point(aes(Time_s,dp_bar),size=0.2) + 
  scale_y_continuous(trans='log10') + 
  ggtitle('Semi-log-plot of pressure change over time') + 
  theme_bw()
```
  
Data is extremely noisy. Not sure how to deal with this at this time of night.  
  
In principle, the experiment is very easy to set up and can be done within one hour including introduction, setup and clean-up. However, unless we assume a linear relationship in the semi-logplot I don't see how the students can evaluate this data.  


# Recovery test  
  
```{r recovery-test-raw, echo=FALSE, message=FALSE, warning=FALSE}
# Get data into shape
data_reco <- read.table('RecoveryTest_200903.csv', sep=';', skip=5,
                        na.strings='#NV', header=TRUE, 
                        col.names=c('Time_p','p_bar','Time_T','T_degC','X')) %>%
  select(-X) %>%
  mutate(Time_p=as.POSIXct(Time_p,format='%d.%m.%Y %H:%M:%OS'),
         Time_T=as.POSIXct(Time_T,format='%d.%m.%Y %H:%M:%OS')) %>%
  drop_na()

ggplot(data_reco) +
  geom_point(aes(Time_p,p_bar),size=0.2) + 
  ggtitle('Raw data') + 
  theme_bw()
```
```{r recovery-test, echo=FALSE}
# Process time series for evaluation
# Process time series for evaluation
data_reco <- data_reco %>%
  mutate(label=if_else(Time_p<=as.POSIXct("2020-09-03 16:22"),'baseline',
                       if_else(Time_p>=as.POSIXct("2020-09-03 16:24"),'test',
                       'NA')))

dp_reco <- data_reco %>%
  filter(label=='test') %>%
  select(Time_p,p_bar) %>%
  mutate(dp_bar=p_bar-min(p_bar),
         dt=c(0,diff(Time_p,lag=1)),
         Time_s=cumsum(dt)) %>%
  filter(Time_s>0) %>%
  filter(dp_bar>0)

ggplot(dp_reco) +
  geom_point(aes(Time_s,dp_bar*1000),size=0.2) + 
  scale_x_continuous(trans='log10') + 
  scale_y_continuous(trans='log10') + 
  ggtitle('Double-log-plot of recovery curve') + 
  ylab('dp [mbar]') + 
  xlab('Time [s]') + 
  theme_bw()
```
  
A pumping/recovery test can be done with small student groups within 1hour including introduction, setup and clean-up.   
  
Which method is suited to evaluate the recovery curve?

# Dilution test  

```{r dilution-test-raw, echo=FALSE, message=FALSE, warning=FALSE}
# Get data into shape
data_dilu <- read.table('Dilution_test_200903.CSV', sep=';', header=TRUE,
                        colClasses=c(NULL,NULL,NULL,'character','character',
                                     'character','character','character',
                                     'character','character',NULL,NULL,NULL,
                                     NULL,NULL)) %>%
  select(Date.Time,Value,Unit,Mode,Value2,Unit2,Mode2) %>%
  mutate(Time=as.POSIXct(Date.Time,format='%d.%m.%Y %H:%M:%OS'),
         Value=as.numeric(Value)) %>%
  select(-Date.Time) %>%
  drop_na()

ggplot(data_dilu) +
  geom_point(aes(Time,Value),size=0.2) + 
  ggtitle('Raw data') + 
  ylab('EC [micro S/cm]') +
  theme_bw()

```
  
A full dilution test cannot be done within one hour, maybe partial recovery can be achieved after 7hrs. 
